Modelling the Lymphatic Metastatic Progression Pathways of OPSCC from Multi-Institutional Datasets

### 2022-12-21 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{center}
    \begin{tabular}{|l|l|l|l|}
        \hline
        \textbf{Graph} & \textbf{-- BIC/2} & \textbf{max. llh} & \textbf{mean llh} \\
        \hline
        base graph    & \variable{output/bg_BIC.txt} & \variable{output/bg_max_llh.txt} & \variable{output/bg_mean_llh.txt} \\
        winning graph & \variable{output/wg_BIC.txt} & \variable{output/wg_max_llh.txt} & \variable{output/wg_mean_llh.txt} \\
        \hline
    \end{tabular}
\end{center}

>>>>

\begin{table}
    \centering
    \variable{output/results_table.tex}
    \caption{Model comparison results from the base and the winning graph.}
    \label{table:evidence}
\end{table}
